<!--
Update the file paths as needed throughout
-->

<!--
Not all case studies will need a Data Exploration subsection
-->

<!--
At the end of this section, save incremental data (if changes were made) so that users can pause and come back later
-->

# **Data Exploration**
***

If you have been following along but stopped, we could load our imported data like so:

```{r}
load(here::here("data", "imported", "pm25_data_imported.rda"))
```

***
<details> <summary> If you skipped the data import section click here. </summary>

An RDA version (stands for R data) of the data can be found [here](https://github.com//opencasestudies/ocs-bp-co2-emissions/tree/master/data/imported) or slightly more directly [here](https://raw.githubusercontent.com/opencasestudies/ocs-bp-co2-emissions/master/data/imported/co2_data_imported.rda). Download this file and then place it in your current working directory within a subdirectory called "imported" within a directory called "data" to use the following code. We used an RStudio project and the [`here` package](https://github.com/jennybc/here_here) to navigate to the file more easily.

```{r, eval=FALSE}
load(here::here("data", "imported", "co2_data_imported.rda"))
```

</details>
***

<!--
Use this section to walk through any exploration of the dataset conducted pre-analysis.
-->
