# **Data Analysis**
***

If you have been following along but stopped, we could load our wrangled data like so:

```{r}
load(here::here("data", "wrangled", "wrangled_data.rda"))
```

***
<details> <summary> If you skipped the data import section click here. </summary>

An RDA file (stands for R data) of the data can be found [here](https://github.com//opencasestudies/ocs-bp-co2-emissions/tree/master/data/wrangled) or slightly more directly [here](https://raw.githubusercontent.com/opencasestudies/ocs-bp-co2-emissions/master/data/wrangled/wrangled_data.rda). Download this file and then place it in your current working directory within a subdirectory called "wrangled" within a subdirectory called "data" to use the following code. We used an RStudio project and the [`here` package](https://github.com/jennybc/here_here) to navigate to the file more easily.


```{r}
load(here::here("data", "wrangled", "wrangled_data.rda"))
```

</details>
***

:::{.think_question}
::::{.think_question_header}
Question opportunity
::::
::::{.inner_block}
Pose a question about the data analysis.
<details><summary>Answer</summary>
You can use a collapsible details section to provide an answer
</details>
::::
:::

::: {.column-margin}
We might use a column margin note to add an equation or some other annotation for learners or educators.
:::

<!--
Use this section to walk through the methods and code used in the data analysis step-by-step.
Explain how this analysis helps answer the main questions posed earlier in the case study.
-->

In this section, you may want to provide learners with some guidance on ways to incorporate AI while they are developing their analysis. They may want AI to

* help them debug
* help them refactor code
* help them simplify or suggest ways to validate code

So, we have developed an AI box that you can pop in whenever you want to do something like this. Note, this is using a tabset approach so that one tab provides background, a suggested prompt, and guidance on how to evaluate or validate the AI's responses. The second tab is providing an important disclaimer about AI use within an analysis.

:::{.ai_box}
::::{.ai_box_header}
How to prompt and validate an AI chatbot
::::
::::{.inner_block}

<u>Context:</u>
Provide context here

Note if there is any context (e.g., a script) that the learner should also provide the chatbot in addition to the prompt

<u>Suggested Prompt:</u>

```
Suggested prompt that learners will be able to copy and paste
```

<u>Validation:</u>
Provide guidance to learners on how they should check or validate the response they have received from AI

::::
:::


Finally, you may want to provide information about reproducibility considerations .... this box may be appropriate in several places throughout the case study, but perhaps you'll want a note right before summary. Use something like the following for such cases (though you may want to rename the header within `reproducibility_box_header` depending on your specific use case):

:::{.reproducibility_box}
::::{.reproducibility_box_header}
Reproducibility consideration / connection
::::
::::{.inner_block}
Here you'll spotlight the reproducibility consideration or thought...This could be a note about needing a specific script or container or what reproducibility concept this is related to (e.g., file management, etc.)
::::
:::

***
