# **Data Analysis**
***

If you have been following along but stopped, we could load our wrangled data like so:

```{r}
load(here::here("data", "wrangled", "wrangled_data.rda"))
```

***
<details> <summary> If you skipped the data import section click here. </summary>

An RDA file (stands for R data) of the data can be found [here](https://github.com//opencasestudies/ocs-bp-co2-emissions/tree/master/data/wrangled) or slightly more directly [here](https://raw.githubusercontent.com/opencasestudies/ocs-bp-co2-emissions/master/data/wrangled/wrangled_data.rda). Download this file and then place it in your current working directory within a subdirectory called "wrangled" within a subdirectory called "data" to use the following code. We used an RStudio project and the [`here` package](https://github.com/jennybc/here_here) to navigate to the file more easily.


```{r}
load(here::here("data", "wrangled", "wrangled_data.rda"))
```

</details>
***

:::{.think_question}
::::{.think_question_header}
Question opportunity
::::
::::{.inner_block}
Pose a question about the data analysis.
<details><summary>Answer</summary>
You can use a collapsible details section to provide an answer
</details>
::::
:::

::: {.column-margin}
We might use a column margin note to add an equation or some other annotation for learners or educators.
:::

<!--
Use this section to walk through the methods and code used in the data analysis step-by-step.
Explain how this analysis helps answer the main questions posed earlier in the case study.
-->

***
